---
title: "tigeR"
author: "Guangchuang Yu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
prettydoc::html_pretty:
    toc: false
    theme: cayman
    highlight: github
vignette: >
  %\VignetteIndexEntry{tigeR}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
```
# 1 Signature Discovery
## 1.1 Gini_rank()
By calculating the Gini index of different genes, you can get an overview of the classification efficiency of different genes.
```
Gini_rank()
```
## 1.2 diff_gene()

# 2 Response Prediction
## 2.1 Predict Response using existing Signatures
You can get a overall Signature score matrix of 23 Signatures in tigeR using predict_Signature() function
```
predict_Signature(extract_mtr('MEL_GSE78220'))

```
## 2.2 Predict Response using built-in functions in tigeR
You can use functions build_NB_model, build_SVM_model, build_RF_model, build_CC_model, build_Adaboost_model, build_Logitboost_model, build_Logistics_model to build corresponding machine learning predictive models (naive Bayes models, Support vector machine model, random forest model, Cancerclass model, Adaboost model, Logitboost model, Logistics regression model). 

The SE parameter input to the function is the SummarizedExperiment object in R or a list of Summarized Experiment objects (including expression profile information and patient clinical information); The parameter Signature is a subset of the genes you are interested in; If the parameter rmBE is TRUE, it means that the function needs to remove the batch effect between datasets through the built-in Batch Effect Removal Tool Combat; Parameter response_NR If TRUE, it means that the function is required to automatically convert the patient's drug response (such as PR, NR, SD, etc. to NR (non-responder) or R (Responder)). The function returns a trained model, after which the user can enter the patient's bulk RNA sequencing expression profile, and the model returns the patient's predicted label.

See details in https:://github/YuLab-SMU/tigeR
